### 2023-12-12 main.tex
''

%The  paper is organized as follows.
% \subsubsection*{Organization of the paper}
\paragraph{Organization of the paper}
In Section~\ref{sec1} we define the open multispecies stirring
process on a general graph and provide its Lie algebraic description in terms of $gl(N)$ generators. In Section~\ref{sectionDuality} we prove an absorption duality (Theorem~\ref{thm-duality})
and show that the problem of characterizing the non-equilibrium
steady state can be reduced to the computation of the absorption probabilities similar to the single-species case on the line  \cite{KMP} and for a general graph \cite{ frassek2020duality}. 
% The duality is proved for a system whose spatial structure is described by a general graph.
In Section~\ref{sectionIntegrabiliy}  we consider  the case of the one-dimensional chain with at most one 
particle per site, which is driven out-of-equilbrium by two reservoirs on the left and right boundaries. In this case we obtain a closed-form expression for the stationary correlations (Theorem~\ref{thm-correlations}). Here the computation
% of the absorption probabilities 
relies on the extension of the  Matrix Product Ansatz \cite{derrida1993exact} to multiple species \cite{vanicat2017exact} and the $gl(N)$ invariance of the process in the bulk. Finally in Section~\ref{sec5} we discuss a few extensions 
and generalizations of the model, including instantaneous thermalization limits and reaction-diffusions. In particular, a thermalized boundary-driven version of the multispecies stirring process is introduced, showing that it has an absorbing duality. Moreover, a further interaction mechanism of reaction type is added in order to have closed evolution equation for average particle density (inspired by \cite{casini2022uphill,schutzReaction}). Again, an absorbing duality is proved and the duality function for the thermalized and the reaction diffusion process turns out to be the same of the multispecies stirring process.
\todo{mention that there is an appendix. In particular Appendix B could be interesting to stress.}
% In closing this introduction we mention that we are currently working on the boundary-driven multispecies 
% model with non-compact Lie algebras, both integrable and non-integrable, which will be presented in a 
% future paper. 
% \todo{I prefer to remove this sentence}

@@

The particles have a {\em type} (sometimes called {\em species} or {\em color})
which can take $N-1$ values.
Then, the dynamics has two parts: 
\item
on each edge of the graph, any two types of particles are swapped at rate $1$;
moreover a particle of any type and a hole are also swapped at rate $1$;\todo{explain what is a hole... Maybe stress that there can be at max $\nu$ holes per site?}
\item
on each vertex $x$ of the graph, a particle of type $a \in \{1,\ldots,N-1\}$ is created  at rate $\alpha_a^x >0$;
additionally a particles of any type is replaced with a
particle of type $a$ at rate $\alpha_a^x >0$ and it is removed at rate $\alpha_N^x >0$.
The swap dynamics taking place on the edges is of Kawasaki-type 
with $N$ conservation laws
(the total number of particles of each type). 
The site-dynamics is instead of Glauber-type. 
In the long-time limit, a so-called non-equilibrium
steady state sets in.
%\noindent
%\begin{remark}
%\label{hole}
%In the following we will often consider type $N$ as a distinguished type
%(called `holes'), whose number at each site is fixed by the numbers of particles 
%of the remaining $N-1$ types. 
% It is interesting to observe that, in case we stop distinguishing the types of the ``true'' particles of types 
% (those of types $\{1,\ldots,N-1\}$), we retrieve the 
% boundary-driven version of the partial symmetric exclusion process \cite{schutzSandow,carinci2013duality}.
In the case $N=2$, we retrieve the  boundary-driven version of the symmetric exclusion process \cite{schutzSandow,carinci2013duality}.
% \todo{I would prefer to say this is for N=2}
%The choice of type $N$ for the distinguished type is arbitrary and does not affect
%the results. However, we shall see in Section~\ref{sectionDuality}, that
%the dual process breaks the symmetry.
%In particular, in the  long-time limit the dual process has only particles of type $N$ on the graph.
%Interpreting type $N$ as an hole, one can then say that the dual process voids the graph.   
%\todo{It is misleading to have to different interpretations. Like what is the number of particles per site? Another confusion is for the reservoirs/open boundaries... Is it the same on general graph?}
%{\color{blue} First question: Do you mean that we should specify it like "the maximal occupancy at each site is..."?\\
%Second question: I think yes. The concept of boundary is general, not only for the chain}

@@

\todo{changed to big indices. OK?}

@@

\todo{explain extra index }  

@@

Observing now that $c_{x}(1-\delta_{\tau_{x},N})$ can be replaced by  $c_{x}-\delta_{\tau_{x},N}$, we finally have
\begin{equation}\label{elementsABS}
	\begin{split}
		\Psi^{'}(\bm{\tau})=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}\dt
	\end{split}
\end{equation} 
\begin{flushright}
    $\square$
\end{flushright}
\begin{remark} By changing the summation indices from $c_x\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}^{'}\in \{0,1-\delta_{\tau_{x},N}\}$ and by  the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as 
\begin{equation}\label{ABS_1}
	\Psi^{'}(\bm{\tau})=\sum_{c^{'}_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c^{'}_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{(L+1-\sum_{x=1}^{L}c^{'}_{x})!}{(L+1)!}\prod_{x=1}^{L}\left((\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(2+L-x-\sum_{j=x}^{L}c^{'}_{j}\right)\right)^{c^{'}_{x}}\beta_{\tau_{x}}^{(1-c^{'}_{x}-\delta_{\tau_{x},N})}
\end{equation}
where we used the fact that 
\begin{equation}
	\left(1+\sum_{j=x}^{L}c_{j}\right) =\left(2+L-x-\sum_{j=x}^{L}c^{'}_{j}\right)\dt
\end{equation}
Equation \eqref{ABS_1} will be useful in the following. 
\end{remark}
\subsubsection{Closed formula for correlations}\label{correlation-section}
We consider $m\in \{1,\ldots,L\}$ sites with coordinates $x_{1},\ldots,x_{m}\in \{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,m-1\}$. We fix $a_{k}\in\{1,\ldots,N-1\}$ and we would like to compute
\begin{equation}
	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle\dt%=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
\end{equation}
We fix the dual configuration $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, corresponding to a vector $|\bm{\xi}\rangle$, and we have 
\begin{equation}
	\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}=D(\bm{\tau},\bm{\xi})\dt
\end{equation}
Thus it follows that 
\begin{align}
	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=&\sum_{\bm{\tau}\in \Omega^{'}}D(\bm{\tau},\bm{\xi})\langle\bm{\tau}|\Psi\rangle
	=\sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle\dt
\end{align}
We denote by $|\hat{\bm{\xi}}\rangle=|\xi^{1},\ldots,\xi^{L}\rangle$, i.e. the vector constructed from $|\bm{\xi}\rangle$ by removing the components at sites $0$ and $L+1$. Recalling that {\color{blue} in the case $\nu=1$, since the matrix $R_{x}$ defined in \eqref{Revmatrix} reduces to the identity, we have that the matrix $d_{x}$ defined in \eqref{bulkElementDualityMatrix} becomes
\begin{equation}
	d_{x}=\exp{(\sum_{a=1}^{N-1}e_{aN}^{x})}
	\end{equation} then, considering equation \eqref{transformationV}, the following holds}
\begin{equation}
	S_{1}^{T}=\prod_{x=1}^{L}d_{x}
\end{equation}  
{\color{blue}As a consequence we have that }
\begin{equation}
	\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle=\langle \bm{\tau}|D|\bm{\xi}\rangle \dt
\end{equation}
Therefore, it follows that, using the resolution of the identity
\begin{align}
\label{corr-psi1}
	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=& \sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
	=\sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\langle\bm{\tau}|\Psi\rangle\nonumber\\
	=&\sum_{\bm{\tau}\in \Omega^{'}}\langle \hat{\bm{\xi}}|S_{1}|\bm{\tau}\rangle\langle\bm{\tau}|\Psi\rangle
	=\langle \hat{\bm{\xi}}|S_{1}|\Psi\rangle
	=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle\dt
\end{align}

Using $\Psi^{'}(\bm{\tau})$ in \eqref{ABS_1} we have 
\begin{align}
	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=&\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{(L+1-\sum_{a=1}^{m}c_{a})!}{(L+1)!}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\nonumber\\
	=&\sum_{c_{1},\ldots,c_{m}=0}^{1}
	f(c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\co
\end{align}
where in the last equality we have used the definition of \eqref{powerCoeffNOspec} and \eqref{powerCoeffSpecies}.
As a last step, using the binomial theorem, we rewrite the previous expression as a polynomial in the boundary densities: 
\begin{align}
	&\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]\nonumber\\=&
	\sum_{c_{1},\ldots,c_{m}=0}^{1}
	f(c_{1},\ldots,c_{m})\prod_{k=1}^{m}\left(\sum_{t_{k}=0}^{c_{k}}(-1)^{c_{k}-t_{k}}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\right)\nonumber\\
	=&\sum_{c_{1},\ldots,c_{m}=0}^{1}
	f(c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\left(\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(x_{j},c_{j},\ldots,c_{m})\right)\nonumber\\
%	=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
%	\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}\alpha_{s_{k}}^{t_{k}}\beta_{s_{k}}^{1-t_{k}}\right)\left(\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(x_{j},c_{j},\ldots,c_{m})\right)\nonumber\\
	=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}(-1)^{c_{k}-t_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\right)\dt
\end{align}
From third to fourth line we have changed the summation order. Therefore, comparing the above formula and \eqref{absProbabilitiesIntegrable}, we can read off the absorption probabilities given in \eqref{abs-probabilities}.
\begin{flushright}
	$\square$
\end{flushright}

@@

\textbf{Proof of formula \eqref{correlations-SSEP}:} Starting from \eqref{exactCorrelations} we exploit indistinguishability\todo{can we just say $N=2$ as we discussed several times now} of particles and we introduce $q=\sum_{k=1}^{m}c_{x_{k}}$. There are many values of $c$'s that give the same $q$, therefore we define {\color{blue} $q$ labels denoted by } %labels denoted by $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ such that  

@@

To each of these label we associate the coordinates $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$ that are such $c_{x_{\ell_{k}}}=1$ for all $k\in \{1,\ldots,q\}$ and $c_{x}=0$ for $x\notin \{x_{\ell_{1}},\ldots,x_{\ell_{q}}\}$. Therefore, for any fixed $c_{x_{1}},\ldots,c_{x_{m}}$, we find $q$ and $\ell_{1},\ldots,\ell_{q}$ from which we fix $x_{\ell_{1}},\ldots,x_{\ell_{q}}$. Then, we obtain  

@@

\textbf{Proof of formula \eqref{psiII-SSEP}:} We specialize equation \eqref{resulEsteady} to the colour-blind case. \todo{can we just say $N=2$ as we discussed several times now}We introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$. For each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present. Thus, arguing as in the proof of \eqref{correlations-SSEP} and using \eqref{Gamma-product} we have that 

@@

In the colour-blind case we have that \todo{can we just say $N=2$ as we discussed several times now}

@@

	\todo{is the last term in the product?}

@@

	\Lambda_{\text{rev}}^{x}(n^{x})=\frac{\nu!}{\prod_{A=1}^{N}n_{A}^{x}!}p^{\sum_{a=1}^{N-1}n_{a}^{x}}p^{n_{N}^{x}}
\todo{Why not merge sum or is there a typo?}

@@

	\\&\nonumber

@@

	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}

>>>>

%The  paper is organized as follows.
% \subsubsection*{Organization of the paper}
\paragraph{Organization of the paper}
In Section~\ref{sec1} we define the open multispecies stirring
process on a general graph and provide its Lie algebraic description in terms of $gl(N)$ generators. In Section~\ref{sectionDuality} we prove an absorption duality (Theorem~\ref{thm-duality})
and show that the problem of characterizing the non-equilibrium
steady state can be reduced to the computation of the absorption probabilities similar to the single-species case on the line  \cite{KMP} and for a general graph \cite{ frassek2020duality}. 
% The duality is proved for a system whose spatial structure is described by a general graph.
In Section~\ref{sectionIntegrabiliy}  we consider  the case of the one-dimensional chain with at most one 
particle per site, which is driven out-of-equilbrium by two reservoirs on the left and right boundaries. In this case we obtain a closed-form expression for the stationary correlations (Theorem~\ref{thm-correlations}). Here the computation
% of the absorption probabilities 
relies on the extension of the  Matrix Product Ansatz \cite{derrida1993exact} to multiple species \cite{vanicat2017exact} and the $gl(N)$ invariance of the process in the bulk. Finally in Section~\ref{sec5} we discuss a few extensions 
and generalizations of the model, including instantaneous thermalization limits and reaction-diffusions. {\color{blue} The first generalization, is to derive a formula, in terms of the absorption probabilities of the dual process, for the non-equilibrium steady state correlation $\nu\geq 1$, i.e. when more than one particle is allowed at each site. In this situation, integrability is lost and we cannot derive explicit formulas for these absorption probabilities. However, in Appendix \ref{appendix-1pts-general}, we show how to compute the one-point correlation by using the properties of a random walk.} The second generalization is the definition of a thermalized version of the boundary-driven multispecies stirring process. Moreover, we show that it has an absorbing duality  {\color{blue}with the same duality function of the multispecies stirring process (the details of the proof are reported in Appendix \ref{appendix-dualityThermalized}). Finally, the third generalization is the introduction of an "ad-hoc" interaction mechanism of reaction type, in order to have closed evolution equation for average particle density (inspired by \cite{casini2022uphill,schutzReaction})}. {\color{blue}We report the details of the computations for the closure of the average density evolution equation in Appendix \ref{appendix-RD}}. Again, an absorbing duality is proved and the duality function turns out to be the same of the multispecies stirring process. 
\todo{mention that there is an appendix. In particular Appendix B could be interesting to stress.}
% In closing this introduction we mention that we are currently working on the boundary-driven multispecies 
% model with non-compact Lie algebras, both integrable and non-integrable, which will be presented in a 
% future paper. 
% \todo{I prefer to remove this sentence}

@@

The particles have a {\em type} (sometimes called {\em species} or {\em colour})
which can take $N-1$ values. {\color{blue}This means that at each site there are $\nu$ available places (called \textit{holes}) that can be either occupied by particles or not. As a consequence, each site can be totally empty (when no particles are present and thus $\nu$ holes are available), totally occupied (when $\nu$ particles, of any type, are present and thus no holes are there) or partially occupied (when some of the holes are occupied and some are available). These situations can be described by introducing the \textit{exclusion constraint} that tells that, at each site and at any time, the sum of the number of particles of any type and of the number of holes is $\nu$.}

Then, the dynamics has two parts: 
\begin{itemize}
\item
on each edge of the graph, any two types of particles are swapped at rate $1$;
moreover a particle of any type and a hole are also swapped at rate $1$;\todo{explain what is a hole... Maybe stress that there can be at max $\nu$ holes per site?}
\item
on each vertex $x$ of the graph, a particle of type $a \in \{1,\ldots,N-1\}$ is created  at rate $\alpha_a^x >0$;
additionally a particles of any type is replaced with a
particle of type $a$ at rate $\alpha_a^x >0$ and it is removed at rate $\alpha_N^x >0$.
\end{itemize}
The swap dynamics taking place on the edges is of Kawasaki-type 
with $N$ conservation laws
(the total number of particles of each type). 
The site-dynamics is instead of Glauber-type. 
In the long-time limit, a so-called non-equilibrium
steady state sets in.
%\noindent
%\begin{remark}
%\label{hole}
%In the following we will often consider type $N$ as a distinguished type
%(called `holes'), whose number at each site is fixed by the numbers of particles 
%of the remaining $N-1$ types. 
% It is interesting to observe that, in case we stop distinguishing the types of the ``true'' particles of types 
% (those of types $\{1,\ldots,N-1\}$), we retrieve the 
% boundary-driven version of the partial symmetric exclusion process \cite{schutzSandow,carinci2013duality}.
In the case $N=2$, we retrieve the  boundary-driven version of the symmetric exclusion process \cite{schutzSandow,carinci2013duality}.
% \todo{I would prefer to say this is for N=2}
%
%The choice of type $N$ for the distinguished type is arbitrary and does not affect
%the results. However, we shall see in Section~\ref{sectionDuality}, that
%the dual process breaks the symmetry.
%In particular, in the  long-time limit the dual process has only particles of type $N$ on the graph.
%Interpreting type $N$ as an hole, one can then say that the dual process voids the graph.   
%
%\end{remark}
%\todo{It is misleading to have to different interpretations. Like what is the number of particles per site? Another confusion is for the reservoirs/open boundaries... Is it the same on general graph?}
%{\color{blue} First question: Do you mean that we should specify it like "the maximal occupancy at each site is..."?\\
%Second question: I think yes. The concept of boundary is general, not only for the chain}

@@

\todo{changed to big indices. OK?[YES]}

@@

\todo{explain extra index [Is the explanation of the remark 4 enough?]}  

@@

Observing now that $c_{x}(1-\delta_{\tau_{x},N})$ can be replaced by  $c_{x}-\delta_{\tau_{x},N}$, we finally have
\begin{equation}\label{elementsABS}
	\begin{split}
		\Psi^{'}(\bm{\tau})=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}\dt
	\end{split}
\end{equation} 
\begin{flushright}
    $\square$
\end{flushright}
\begin{remark} By changing the summation indices from $c_x\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}^{'}\in \{0,1-\delta_{\tau_{x},N}\}$ and by  the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as 
\begin{equation}\label{ABS_1}
	\Psi^{'}(\bm{\tau})=\sum_{c^{'}_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c^{'}_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{(L+1-\sum_{x=1}^{L}c^{'}_{x})!}{(L+1)!}\prod_{x=1}^{L}\left((\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(2+L-x-\sum_{j=x}^{L}c^{'}_{j}\right)\right)^{c^{'}_{x}}\beta_{\tau_{x}}^{(1-c^{'}_{x}-\delta_{\tau_{x},N})}
\end{equation}
where we used the fact that 
\begin{equation}
	\left(1+\sum_{j=x}^{L}c_{j}\right) =\left(2+L-x-\sum_{j=x}^{L}c^{'}_{j}\right)\dt
\end{equation}
Equation \eqref{ABS_1} will be useful in the following. 
\end{remark}
\subsubsection{Closed formula for correlations}\label{correlation-section}
We consider $m\in \{1,\ldots,L\}$ sites with coordinates $x_{1},\ldots,x_{m}\in \{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,m-1\}$. We fix $a_{k}\in\{1,\ldots,N-1\}$ and we would like to compute
\begin{equation}
	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle\dt%=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
\end{equation}
We fix the dual configuration $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, corresponding to a vector $|\bm{\xi}\rangle$, and we have 
\begin{equation}
	\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}=D(\bm{\tau},\bm{\xi})\dt
\end{equation}
Thus it follows that 
\begin{align}
	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=&\sum_{\bm{\tau}\in \Omega^{'}}D(\bm{\tau},\bm{\xi})\langle\bm{\tau}|\Psi\rangle
	=\sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle\dt
\end{align}
We denote by $|\hat{\bm{\xi}}\rangle=|\xi^{1},\ldots,\xi^{L}\rangle$, i.e. the vector constructed from $|\bm{\xi}\rangle$ by removing the components at sites $0$ and $L+1$. Recalling that {\color{blue} in the case $\nu=1$, since the matrix $R_{x}$ defined in \eqref{Revmatrix} reduces to the identity, we have that the matrix $d_{x}$, defined in \eqref{bulkElementDualityMatrix}, becomes
\begin{equation}
	d_{x}=\exp{(\sum_{a=1}^{N-1}e_{aN}^{x})}\dt
	\end{equation} Then, considering equation \eqref{transformationV}, the following holds}
\begin{equation}
	S_{1}^{T}=\prod_{x=1}^{L}d_{x}
\end{equation}

\todo{double check and ref to $d_x$ and say that R is id [DONE]}
{\color{blue}As a consequence we have that }
\begin{equation}
	\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle=\langle \bm{\tau}|D|\bm{\xi}\rangle \dt
\end{equation}
Therefore, it follows that, using the resolution of the identity
\begin{align}
\label{corr-psi1}
	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=& \sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
	=\sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\langle\bm{\tau}|\Psi\rangle\nonumber\\
	=&\sum_{\bm{\tau}\in \Omega^{'}}\langle \hat{\bm{\xi}}|S_{1}|\bm{\tau}\rangle\langle\bm{\tau}|\Psi\rangle
	=\langle \hat{\bm{\xi}}|S_{1}|\Psi\rangle
	=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle\dt
\end{align}

Using $\Psi^{'}(\bm{\tau})$ in \eqref{ABS_1} we have 
\begin{align}
	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=&\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{(L+1-\sum_{a=1}^{m}c_{a})!}{(L+1)!}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\nonumber\\
	=&\sum_{c_{1},\ldots,c_{m}=0}^{1}
	f(c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\co
\end{align}
where in the last equality we have used the definition of \eqref{powerCoeffNOspec} and \eqref{powerCoeffSpecies}.
As a last step, using the binomial theorem, we rewrite the previous expression as a polynomial in the boundary densities: 
\begin{align}
	&\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]\nonumber\\=&
	\sum_{c_{1},\ldots,c_{m}=0}^{1}
	f(c_{1},\ldots,c_{m})\prod_{k=1}^{m}\left(\sum_{t_{k}=0}^{c_{k}}(-1)^{c_{k}-t_{k}}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\right)\nonumber\\
	=&\sum_{c_{1},\ldots,c_{m}=0}^{1}
	f(c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\left(\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(x_{j},c_{j},\ldots,c_{m})\right)\nonumber\\
%	=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
%	\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}\alpha_{s_{k}}^{t_{k}}\beta_{s_{k}}^{1-t_{k}}\right)\left(\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(x_{j},c_{j},\ldots,c_{m})\right)\nonumber\\
	=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}(-1)^{c_{k}-t_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\right)\dt
\end{align}
From third to fourth line we have changed the summation order. Therefore, comparing the above formula and \eqref{absProbabilitiesIntegrable}, we can read off the absorption probabilities given in \eqref{abs-probabilities}.
{\color{blue}\begin{remark}
From equation \eqref{corr-psi1}, we observe that, for any configuration $\bm{\tau}$ that has at least a particle, we interpret the coefficient $\Psi^{'}(\tau)$ of the vector $|\Psi^{'}\rangle$ as a correlation. However, this interpretation does not cover the case when $\bm{\tau}=(N,\ldots,N)$, i.e. when no particles are present in the configuration. In Appendix \ref{subsection-interpretationPSIp} we show that, for any configuration $\bm{\tau}\in \Omega^{'}$ we have 
\begin{equation}\label{interpretation-PsiP}
	\Psi^{'}(\bm{\tau})=\mathbb{E}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{Y_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]\dt
\end{equation} 
The above formula \eqref{interpretation-PsiP} allows to interpret these coefficients as marginals of the non-equilibrium steady distribution $\mu$. As a by-product, we obtain that $\Psi^{'}(N,\ldots,N)=1$, i.e. it is the normalization of the measure $\mu$. In particular, these marginal are the non-equilibrium steady state correlations as soon as the configuration $\bm{\tau}$ does contain at least a particle. 
\end{remark} }
\begin{flushright}
	$\square$
\end{flushright}

@@

\textbf{Proof of formula \eqref{correlations-SSEP}:} Starting from \eqref{exactCorrelations} we exploit {\color{blue} the fact that $N=2$, i.e. that each site can be either occupied by a particle or empty.}\todo{can we just say $N=2$ as we discussed several times now [DONE]} We introduce $q=\sum_{k=1}^{m}c_{x_{k}}$. There are many values of $c$'s that give the same $q$, therefore we define {\color{blue} $q$ labels denoted by } %labels denoted by $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ such that  

@@

To each of these label we associate the coordinates $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$ that are such that $c_{x_{\ell_{k}}}=1$ for all $k\in \{1,\ldots,q\}$ and $c_{x}=0$ for $x\notin \{x_{\ell_{1}},\ldots,x_{\ell_{q}}\}$. Therefore, for any fixed $c_{x_{1}},\ldots,c_{x_{m}}$, we find $q$ and $\ell_{1},\ldots,\ell_{q}$ from which we fix $x_{\ell_{1}},\ldots,x_{\ell_{q}}$. Then, we obtain  

@@

\textbf{Proof of formula \eqref{psiII-SSEP}:} We specialize equation \eqref{resulEsteady} to the {\color{blue} $N=2$ case}. \todo{can we just say $N=2$ as we discussed several times now [DONE]}We introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$. For each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present. Thus, arguing as in the proof of \eqref{correlations-SSEP} and using \eqref{Gamma-product} we have that 

@@

In the {\color{blue} $N=2$} case we have that \todo{can we just say $N=2$ as we discussed several times now[DONE]}

@@

	\todo{is the last term in the product?[Correct, I have done it also in appendix C]}

@@

	\Lambda_{\text{rev}}^{x}(n^{x})=\frac{\nu!}{\prod_{A=1}^{N}n_{A}^{x}!}p^{\sum_{a=1}^{N-1}n_{a}^{x}}p_{N}^{n_{N}^{x}}
\todo{Why not merge sum or is there a typo? [There was a typo]}

@@

	\\
	\times &\nonumber

@@

	\\\times &
	\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{\alpha_{N}}\right)^{r_{a}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}\right)
